Unbiased pangenome graphs

### 2022-05-15 manuscript/main.tex
nsf ppos funding
update ODGI citation

In table \ref{tab:experiments} we provide input and constructed graph parameters for a single parameter setting of \textit{wfmash} and \textit{seqwish}, obtaining graph statistics with the ODGI toolkit \citep{Guarracino_2021}.
Figure \ref{fig:experiments} displays runtime versus graph size relative to the average input genome length across the range of parameters chosen for each pangenome.
These provide a consistent set of insights.
Reducing the sensitivity of alignments by increasing the identity threshold results in larger graphs.
Filtering short matches results in larger graphs too, and for higher divergence collections of genomes, like \textit{H. pylori}, tends to obliterate much of the homology information in the pangenome graph.
This is visible from the fact that the "graph length / average genome length" ratio grows strongly as $k$ increases.
Such a reduction of the size of the set of matches considered for graph inductions also greatly reduces runtime.
In all cases, we find that the initial alignment step takes longer than graph induction.

>>>>

In table \ref{tab:experiments} we provide input and constructed graph parameters for a single parameter setting of \textit{wfmash} and \textit{seqwish}, obtaining graph statistics with the ODGI toolkit \citep{Guarracino2022}.
Figure \ref{fig:experiments} displays runtime versus graph size relative to the average input genome length across the range of parameters chosen for each pangenome.
These provide a consistent set of insights.
Reducing the sensitivity of alignments by increasing the identity threshold results in larger graphs.
Filtering short matches results in larger graphs too, and for higher divergence collections of genomes, like \textit{H. pylori}, tends to obliterate much of the homology information in the pangenome graph.
This is visible from the fact that the "graph length / average genome length" ratio grows strongly as $k$ increases.
Such a reduction of the size of the set of matches considered for graph inductions also greatly reduces runtime.
In all cases, we find that the initial alignment step takes longer than graph induction.
